---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TFGproject

The goal of TFGproject is to provide an easy and robust implementation of the Marascuilo procedure for multiple comparisons of proportions, compliant with standard S3 class architecture.

## Installation

You can install the development version of TFGproject from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("Rumii18/TFGproject")
```

## Example

This is a basic example which shows how to solve a common problem using the package's generic methods:

```{r example}
library(TFGproject)

# 1. Create a sample dataset
df_ejemplo <- data.frame(
  Ciudad = c(rep("Cordoba", 150), rep("Villa Maria", 75), rep("Rio IV", 75)),
  Opinion = c(
    rep("De acuerdo", 115), rep("En desacuerdo", 35),
    rep("De acuerdo", 53), rep("En desacuerdo", 22),
    rep("De acuerdo", 40), rep("En desacuerdo", 35)
  )
)

# 2. Run the Marascuilo test
resultados <- marascuilo_test(
  df = df_ejemplo, 
  col_grupo = "Ciudad", 
  col_respuesta = "Opinion", 
  valor_exito = "De acuerdo"
)

# 3. Print the results (using the custom print method)
resultados

# 4. Visualize the comparisons (using the generic plot method)
plot(resultados)
```