---
title: "Tutorial: Marascuilo Procedure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial: Marascuilo Procedure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The `TFGproject` package provides an easy-to-use implementation of the Marascuilo procedure. This test is typically used after a significant Chi-square test to determine exactly which groups differ from each other when comparing multiple proportions.

## Setup

First, load the package into your environment:

```{r setup}
library(TFGproject)
```

## Example Data

Let's create a sample dataset representing a survey about a specific opinion across three different cities:

```{r data}
df_ejemplo <- data.frame(
  Ciudad = c(rep("Cordoba", 150), rep("Villa Maria", 75), rep("Rio IV", 75)),
  Opinion = c(
    rep("De acuerdo", 115), rep("En desacuerdo", 35),
    rep("De acuerdo", 53), rep("En desacuerdo", 22),
    rep("De acuerdo", 40), rep("En desacuerdo", 35)
  )
)
```

## Running the Test

We use the `marascuilo_test()` function. We need to specify the dataset, the grouping column, the response column, and the specific value that represents a "success" (in this case, "De acuerdo").

```{r test}
resultados <- marascuilo_test(
  df = df_ejemplo, 
  col_grupo = "Ciudad", 
  col_respuesta = "Opinion", 
  valor_exito = "De acuerdo"
)
```

## Results and Visualization

Because the package uses a custom S3 class architecture, you can simply print the object to see the results and which comparisons are statistically significant:

```{r print}
resultados
```

To visually interpret these results, use the generic `plot()` function. It will automatically generate a `ggplot2` chart showing the confidence intervals for each pair of differences:

```{r plot, fig.width=7, fig.height=5}
plot(resultados)
```